Visualizations for the manuscript

### 2022-04-28 metanalysis_visualization/manuscript_Figures.Rmd
fix rbinom bug, change bootstrap to 10000 and change time range for plots

```{r}
# cut-off dates used in the analysis, these should not be changed
time_period <-"months" #possible values: days, weeks, months
#history_start_date <- as.Date("2019-01-01")
#history_end_date <- as.Date("2021-05-31")
pandemic_start_date <- as.Date("2020-03-15")
start_date_plots <- as.Date("2019-01-01")
end_date_plots <- as.Date("2021-05-31")
```

@@

# Filter by dates
```{r}
start_date_plots <- as.Date("2019-01-01")
end_date_plots <- as.Date("2021-05-31")

@@

```{r}
# Call function from another file : bootstrap.R
bootstrap_size <- 1000
binom_proportion <- function(n, prob, size) {
  (rbinom(n, size, prob) / size) * 100
}

bootstrapping_slopes <- function(df,
                                 group_name,
                                 bootstrap_size,
                                 count = "count_icd",
                                 percentage = "percentage") {
  bootstrapped_timepoints <- mapply(
    binom_proportion,
    n = bootstrap_size,
    size = df[[count]],
    prob = df[[percentage]]/100)
  bootstrapped_sample_list <- vector(mode = "list", length = bootstrap_size)
  bootstrapped_coefficients_list <- vector(mode = "list", length = bootstrap_size)
  for (iteration in 1:bootstrap_size) {
    df_iteration <- data.frame(period = df$period,
                               time = df$time,
                               percentage = bootstrapped_timepoints[iteration, ])
    ts_linear_percent <- lm(as.formula(paste0(percentage, "~ period * time")), df_iteration)
    linear_model <- broom::tidy(ts_linear_percent) %>%
      filter(term %in% c("time", "periodduring_pandemic:time"))
    coefficients <- linear_model$estimate
    names(coefficients) <- linear_model$term
    bootstrapped_coefficients_list[[iteration]] <- coefficients
    df_iteration$predicted <- predict(ts_linear_percent)
    df_iteration$time_p <- df$time_p
    bootstrapped_sample_list[[iteration]] <- df_iteration
  }
  bootstrapped_fitted_df <- bind_rows(bootstrapped_sample_list, .id = "iteration") %>%
    bind_cols(group_name)
  bootstrapped_coefficients_df <- bind_rows(bootstrapped_coefficients_list,
                                            .id = "iteration") %>%
    bind_cols(group_name)
  return(list(bootstrapped_coefficients_df,
              bootstrapped_fitted_df))
}
```

@@

ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("boostrapped_all_long.png", height = 20, width = 45, units = "cm")
```

@@

metafor::forest(model_meta_siteid,
                slab = trends_siteid$plotsLabel,
                plim = c(1, NA),
                order = "obs",
                cex=0.7,
                showweights = TRUE,
                header="Sites",
                mlab="Overall periods' slope differences")
```

@@

forest(model_meta_country, 
       slab = trends_country$country,
       plim = c(1, NA),
       order = "obs", 
       showweights = TRUE,
       header = "Countries",
       mlab = "Overall periods' slope differences")
```

@@

## Using only male, but female and male necessarily yield equal p-values
plot_annotations_sex_df <- annotation_function(
  df_coefficients_boot_sex[df_coefficients_boot_sex$sex == "female", ]
) %>% data.frame(label = ., 
                 plotsLabel = "Female")

# plot_annotations_sex_df <- df_coefficients_boot_sex %>% 
#   group_by(sex) %>% 
#   group_map(annotation_function) %>%
#   paste(str_to_title(names_sex), ., sep = ": ") %>% 
#   as_tibble() %>% 
#   rename(label = value)
# bind_cols(group_names) %>% 
#                rename(label = value) %>% 
#                mutate(label = paste(stringr::str_to_title(sex), label, sep = ": ")) %>% 
#                mutate(plotsLabel = names_site_id)
#              , .keep = TRUE) %>% 
  # group_map( function(df, group_names) group_by(df, plotsLabel) %>%
  #              annotation_function() %>%
               # as_tibble() %>%
               # bind_cols(group_names) %>%
               # rename(label = value) %>%
               # mutate(label = paste(stringr::str_to_title(sex), label, sep = ": ")) %>%
  #              mutate(plotsLabel = names_site_id)
  #            , .keep = TRUE) %>% 
  # set_names(unique(df_coefficients_boot_sex$sex))

@@

```{r bootstrap_plot}
ggplot(bootstrapped_fitted_sex, aes(x = time_p, y = predicted, group = interaction(iteration, period, sex))) +
  # facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = interaction(period, sex)),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value, group = interaction(quantiles, period, sex)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value, group = interaction(period, sex))) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage, group=sex, color = interaction(period, sex)),
             alpha = 1) +
  scale_color_brewer(palette = "Paired") +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  # scale_colour_manual(values = c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C")) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_sex_df,
             aes(label=label),
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  # geom_label(data = plot_annotations_sex_df[["male"]],
  #            aes(label=label),
  #            x = -Inf,
  #            y = 15,
  #            hjust = 0,
  #            vjust = 0,
  #            size = 4,
  #           inherit.aes = FALSE) +
  # ylim(10, 90) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
  subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
  plot.subtitle = element_text(size = 12, face = "italic"))
```

@@

```{r}
disorders_to_select <- c(
  "Anxiety Disorders", 
  "Depressive Disorders", 
  "Feeding and Eating Disorders", 
  "Suicide or Self-Injury"
)

@@

ggplot(bootstrapped_fitted_disorder,
       aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("disorder_group",
             scales = "free_y",
             labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_disorder,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_disorder[quantile_bootstrapped_fitted_disorder$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = filter(perc_disorder_group_total,
                           disorder_group %in% disorders_to_select),
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_disorder_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("boostrapped_disorders.png", height = 14, width = 25, units = "cm")

@@

fig

@@

numberOfCodesPerDisorderGroup %>%
  left_join( country_map ) %>%
  mutate( disorder_group = swr( disorder_group ) )  %>%
  ggplot( aes( x= siteid, y = icd_codes_count, fill = country )) +
  geom_bar( stat = "identity") +
  scale_fill_manual("Country of each site", values = c("USA" = "navy", "France" = "orange")) +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  labs(x ="site identifier", y = "ICD dictionary (number of ICD codes)") +
  scale_x_discrete(limits = positions) +
  theme(axis.text.x=element_text(angle=45,hjust=1, size = 6), 
        strip.text = element_text(size = 7), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        legend.position="bottom") 
```

@@

counts_plot <- counts2 %>% ggplot( aes( x= as.Date( time_p ), y = value, group= group )) +
  geom_point( aes( shape= group, color = group )) +
  facet_wrap2("plotsLabel", axes = "all", scales ="free", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) + 
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "number of patients")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")
counts_plot
ggsave("counts_plot.png",counts_plot, height = 20, width = 32, units = "cm")

@@

counts_agg2 %>% ggplot( aes( x= as.Date( time_p ), y = value, group= group )) +
  geom_point( aes( shape= group, color = group )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "number of patients")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")
```

>>>>

```{r}
# cut-off dates used in the analysis, these should not be changed
time_period <-"months" #possible values: days, weeks, months
#history_start_date <- as.Date("2019-01-01")
#history_end_date <- as.Date("2021-05-31")
pandemic_start_date <- as.Date("2020-03-15")
start_date_plots <- as.Date("2019-02-01")
end_date_plots <- as.Date("2021-04-30")
```

@@

# Filter by dates
```{r}
start_date_plots <- as.Date("2019-02-01")
end_date_plots <- as.Date("2021-04-30")

@@

```{r}
# Call function from another file : bootstrap.R
bootstrap_size <- 10000
binom_proportion <- function(n, prob, size) {
  (rbinom(n, size, prob) / size) * 100
}

bootstrapping_slopes <- function(df,
                                 group_name,
                                 bootstrap_size,
                                 count = "count_icd",
                                 percentage = "percentage") {
  bootstrapped_timepoints <- mapply(
    binom_proportion,
    n = bootstrap_size,
    size = as.integer(df[[count]]),
    prob = df[[percentage]]/100)
  bootstrapped_sample_list <- vector(mode = "list", length = bootstrap_size)
  bootstrapped_coefficients_list <- vector(mode = "list", length = bootstrap_size)
  for (iteration in 1:bootstrap_size) {
    df_iteration <- data.frame(period = df$period,
                               time = df$time,
                               percentage = bootstrapped_timepoints[iteration, ])
    ts_linear_percent <- lm(as.formula(paste0(percentage, "~ period * time")), df_iteration)
    linear_model <- broom::tidy(ts_linear_percent) %>%
      filter(term %in% c("time", "periodduring_pandemic:time"))
    coefficients <- linear_model$estimate
    names(coefficients) <- linear_model$term
    bootstrapped_coefficients_list[[iteration]] <- coefficients
    df_iteration$predicted <- predict(ts_linear_percent)
    df_iteration$time_p <- df$time_p
    bootstrapped_sample_list[[iteration]] <- df_iteration
  }
  bootstrapped_fitted_df <- bind_rows(bootstrapped_sample_list, .id = "iteration") %>%
    bind_cols(group_name)
  bootstrapped_coefficients_df <- bind_rows(bootstrapped_coefficients_list,
                                            .id = "iteration") %>%
    bind_cols(group_name)
  return(list(bootstrapped_coefficients_df,
              bootstrapped_fitted_df))
}
```

@@

ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("figure1_boostrapped_all.png", height = 20, width = 45, units = "cm")
```

@@

metafor::forest(model_meta_siteid,
                slab = trends_siteid$plotsLabel,
                plim = c(1, NA),
                order = "obs",
                cex=0.7,
                showweights = TRUE,
                header="Sites",
                mlab="Overall periods' slope differences")
ggsave("figure2A_metaanalysis_persite.png", height = 20, width = 45, units = "cm")

@@

forest(model_meta_country, 
       slab = trends_country$country,
       plim = c(1, NA),
       order = "obs", 
       showweights = TRUE,
       header = "Countries",
       mlab = "Overall periods' slope differences")
ggsave("figure2B_metaanalysis_country.png", height = 20, width = 45, units = "cm")

@@

## Using only male, but female and male necessarily yield equal p-values
plot_annotations_sex_df <- annotation_function(
  df_coefficients_boot_sex[df_coefficients_boot_sex$sex == "female", ]
) %>% data.frame(label = ., 
                 plotsLabel = "Female")
```

```{r bootstrap_plot}
ggplot(bootstrapped_fitted_sex, aes(x = time_p, y = predicted, group = interaction(iteration, period, sex))) +
  # facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = interaction(period, sex)),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value, group = interaction(quantiles, period, sex)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value, group = interaction(period, sex))) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage, group=sex, color = interaction(period, sex)),
             alpha = 1) +
  scale_color_brewer(palette = "Paired") +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  # scale_colour_manual(values = c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C")) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_sex_df,
             aes(label=label),
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
  subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
  plot.subtitle = element_text(size = 12, face = "italic"))
ggsave("figure4_ITS_sex.png", height = 20, width = 45, units = "cm")

@@

@@

```{r }
disorders_to_select <- c(
  "Anxiety Disorders", 
  "Depressive Disorders", 
  "Feeding and Eating Disorders", 
  "Suicide or Self-Injury"
)

@@

ggplot(bootstrapped_fitted_disorder,
       aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("disorder_group",
             scales = "free_y",
             labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_disorder,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_disorder[quantile_bootstrapped_fitted_disorder$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = filter(perc_disorder_group_total,
                           disorder_group %in% disorders_to_select),
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_disorder_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 8, face = "italic")) 
ggsave("figure3_boostrapped_disorders.png", height = 15, width = 35, units = "cm")

@@

fig
ggsave("figure_supp3_counts_disorder.png", height = 20, width = 45, units = "cm")

@@

numberOfCodesPerDisorderGroup %>%
  left_join( country_map ) %>%
  mutate( disorder_group = swr( disorder_group ) )  %>%
  ggplot( aes( x= siteid, y = icd_codes_count, fill = country )) +
  geom_bar( stat = "identity") +
  scale_fill_manual("Country of each site", values = c("USA" = "navy", "France" = "orange")) +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  labs(x ="site identifier", y = "ICD dictionary (number of ICD codes)") +
  scale_x_discrete(limits = positions) +
  theme(axis.text.x=element_text(angle=45,hjust=1, size = 6), 
        strip.text = element_text(size = 7), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        legend.position="bottom") 
ggsave("figure_supp2_ICDdictionaryQC.png", height = 20, width = 45, units = "cm")

@@

counts_plot <- counts2 %>% ggplot( aes( x= as.Date( time_p ), y = value, group= group )) +
  geom_point( aes( shape= group, color = group )) +
  facet_wrap2("plotsLabel", axes = "all", scales ="free", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) + 
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "number of patients")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")
counts_plot
ggsave("figure_supp1A_counts_per_site.png",counts_plot, height = 20, width = 32, units = "cm")

@@

counts_agg2 %>% ggplot( aes( x= as.Date( time_p ), y = value, group= group )) +
  geom_point( aes( shape= group, color = group )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "number of patients")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")
ggsave("figure_supp1B_counts_all.png",counts_plot, height = 20, width = 32, units = "cm")
